Modelling the emergence of whisker barrels

### 2019-12-20 paper/briefpaper/brief.tex
Explicitly choose 17.8 cm as per guidelines
Tweak acknowl

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{./MainFig.png}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure (Honda-$\delta$; see \cite{senft_mouse_1991}) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection, and two molecular guidance fields ($\rho$). \textbf{B} The strengths of interaction $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41 projections by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of putative barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$, $\epsilon=150$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.5$ (see Movie S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from simulation approaching that obtained from barrels in \textbf{A} (dotted line);  black squares measure the correspondence between the real and simulated barrel shapes, $\eta$ (the product of the sum of squared differences between real and simulated centers and the sum of differences in area; units mm$^4$). \textbf{E} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ at the join ($\epsilon=80$). All scale bars 1mm.}
\label{fig:main}
\end{figure*}

@@

\acknow{The authors thank Jason Berwick at the University of Sheffield for
  access to original rat barrel stains. This work was supported by a
  Collaborative Activity Award, \emph{Cortical Plasticity Within and Across
  Lifetimes}, from the James S.~McDonnell Foundation (grant 220020516).}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=17.8cm]{./MainFig.png}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure (Honda-$\delta$; see \cite{senft_mouse_1991}) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection, and two molecular guidance fields ($\rho$). \textbf{B} The strengths of interaction $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41 projections by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of putative barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$, $\epsilon=150$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.5$ (see Movie S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from simulation approaching that obtained from barrels in \textbf{A} (dotted line);  black squares measure the correspondence between the real and simulated barrel shapes, $\eta$ (the product of the sum of squared differences between real and simulated centers and the sum of differences in area; units mm$^4$). \textbf{E} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ at the join ($\epsilon=80$). All scale bars 1mm.}
\label{fig:main}
\end{figure*}

@@

\acknow{The authors thank Jason Berwick at the University of Sheffield for
  advice and for access to the rat barrel stains used to construct
  Fig.\,1A. This work was supported by a Collaborative Activity Award,
  \emph{Cortical Plasticity Within and Across Lifetimes}, from the James
  S.~McDonnell Foundation (grant 220020516).}
